# Loading packages

```{r}
# loading packages
pacman::p_load(tidyverse, patchwork, ggpubr)
```

# Defining general parameters

```{r}
# defining general parameters
trials <- 120
agents <- 100
```

# Initialising agent functions
## Random Agent

```{r}
# randomAgent (no bias, no noise)

rate <- 0.5

RandomAgent_f <- function(input, rate){
  n <- length(input)
  choice <- rbinom(n, 1, rate)
  return(choice)
}
```

## Win-stay-lose-shift Agent (no noise)

```{r}
# WSLSAgent (no noise)

# as a function
WSLSAgent_f <- function(prevChoice, Feedback){
  if (Feedback == 1) {
    choice = prevChoice
  } else if (Feedback == 0) {
      choice = 1 - prevChoice
      }
  return(choice)
}
```

## Strategy 1: The Strategy of Sai (a heuristic agent) with noise

```{r}
# alternative strategy 1: reverse gambler's fallacy (Sai's strategy). If previous two choices are the same and both win, then switch. If previous two choices are the same and both lose, then stay. Otherwise chose random.

strategy_1 <- function(prevChoice_1, prevChoice_2, feedback_1, feedback_2, rate, noise){
  if (prevChoice_1 == prevChoice_2){
    if ((feedback_1 == 1) & (feedback_2 == 1)) {
    choice = 1 - prevChoice_1
    } else if ((feedback_1 == 0) & (feedback_2 == 0)) {
    choice = prevChoice_1
    } else {
      choice <- rbinom(1, 1, rate)
    }
  } else {
      choice <- rbinom(1, 1, rate)
  }
  if (rbinom(1, 1, noise) == 1) {choice = rbinom(1,1,0.5)}
  return(choice)
}


```

## Strategy 2: Win-switch-lose-stay Agent (with noise)

```{r}
# alternative strategy 2: Win switch lose stay

strategy_2 <- function(prevChoice, Feedback, noise){
  if (Feedback == 1) {
    choice = 1 - prevChoice
  } else if (Feedback == 0) {
      choice = prevChoice
  }
  if (rbinom(1, 1, noise) == 1) {choice = rbinom(1,1,0.5)}
  return(choice)
}

```

# Simulations

## Random vs WSLS

```{r}
# randomagent vs. WSLS
Self <- rep(NA, trials)
Other <- rep(NA, trials)

Self[1] <- RandomAgent_f(1, 0.5)
Other <- RandomAgent_f(seq(trials), rate)
  

for (i in 2:trials) {
  if (Self[i - 1] == Other[i - 1]) {
    Feedback = 1
  } else {Feedback = 0}
  Self[i] <- WSLSAgent_f(Self[i - 1], Feedback)
}

sum(Self == Other)

df <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

ggplot(df) + theme_classic() +
  geom_line(color = "red", aes(trial, Self)) +
  geom_line(color = "blue", aes(trial, Other))
```

## Random vs. Strategy 1

```{r}
# randomagent vs. strategy 1
Self <- rep(NA, trials)
Other <- rep(NA, trials)

Self[1] <- RandomAgent_f(1, 0.5)
Other <- RandomAgent_f(seq(trials), rate)
Self[2] <- RandomAgent_f(1, 0.5)
  

for (i in 3:trials) {
  if (Self[i - 1] == Other[i - 1]) {
    feedback_1 = 1
  } else {feedback_1 = 0}
  if (Self[i - 2] == Other[i - 2]) {
    feedback_2 = 1
  } else {feedback_2 = 0}
  Self[i] <- strategy_1(Self[i - 1], Self[i - 2], feedback_1 = feedback_1, feedback_2 = feedback_2, rate = 0.5, noise = 0.1)
}

sum(Self == Other)

df <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

ggplot(df) + theme_classic() +
  geom_line(color = "red", aes(trial, Self)) +
  geom_line(color = "blue", aes(trial, Other))

```

## Random vs. Strategy 2

```{r}
# randomagent vs. strategy 2
Self <- rep(NA, trials)
Other <- rep(NA, trials)

Self[1] <- RandomAgent_f(1, 0.5)
Other <- RandomAgent_f(seq(trials), rate)
  

for (i in 2:trials) {
  if (Self[i - 1] == Other[i - 1]) {
    Feedback = 1
  } else {Feedback = 0}
  Self[i] <- strategy_2(Self[i - 1], Feedback, noise = 0.1)
}

sum(Self == Other)

df <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

ggplot(df) + theme_classic() +
  geom_line(color = "red", aes(trial, Self)) +
  geom_line(color = "blue", aes(trial, Other))

```

## WSLS vs. Strategy 1

```{r}
# WSLS (self) vs. strategy 1 (other)
Self <- rep(NA, trials)
Other <- rep(NA, trials)

Self[1] <- RandomAgent_f(1, 0.5)
Other[1] <- RandomAgent_f(1, 0.5)
Self[2] <- WSLSAgent_f(prevChoice = Self[1], Feedback = ifelse(Self[1] == Other[1], 1, 0))
Other[2] <- RandomAgent_f(1, 0.5)

for (i in 3:trials) {
  if (Self[i - 1] == Other[i - 1]) {
    feedback_1 = 1
  } else {feedback_1 = 0}
  if (Self[i - 2] == Other[i - 2]) {
    feedback_2 = 1
  } else {feedback_2 = 0}
  
  Self[i] <- WSLSAgent_f(prevChoice = Self[i-1], Feedback = feedback_1)
  Other[i] <- strategy_1(Other[i - 1], Other[i - 2], feedback_1 = 1-feedback_1, feedback_2 = 1-feedback_2, rate = 0.5, noise = 0.1)
}

sum(Self == Other)

df <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

df <- df %>% 
  mutate(cumulativerate = cumsum(Feedback)/seq_along(Feedback))

a <- ggplot(df) + theme_classic() +
  geom_line(color = "red", aes(trial, Self)) +
  geom_line(color = "blue", aes(trial, Other)) +
  ggtitle("WSLS (self) vs. Strategy 1 (other)")

b <- df %>% 
  ggplot(aes(x = trial, y = cumulativerate)) +
  geom_line()+
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  ylim(0,1) +
  theme_classic() +
  ggtitle("WSLS (self = 1) vs. Strategy 1 (other = 0)")

ggarrange(a,b, nrow = 2, ncol = 1)

ggsave("figures/outcome_1_agent_wsls_vs_strategy_1.png")

```

## WSLS vs. Strategy 2

```{r}
# WSLS vs. strategy 2
Self <- rep(NA, trials)
Other <- rep(NA, trials)

Self[1] <- RandomAgent_f(1, 0.5)
Other[1] <- RandomAgent_f(1, 0.5)

for (i in 2:trials) {
  if (Self[i - 1] == Other[i - 1]) {
    Feedback = 1
  } else {Feedback = 0}
  Self[i] <- WSLSAgent_f(Self[i - 1], Feedback)
  Other[i] <- strategy_2(prevChoice = Other[i - 1], Feedback = 1 - Feedback, noise = 0.1)
}

sum(Self == Other)

df <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

df <- df %>% 
  mutate(cumulativerate = cumsum(Feedback)/seq_along(Feedback))

a <- ggplot(df) + theme_classic() +
  geom_line(color = "red", aes(trial, Self)) +
  geom_line(color = "blue", aes(trial, Other)) +
  ggtitle("WSLS (self) vs. Strategy 2 (other)")

b <- df %>% 
  ggplot(aes(x = trial, y = cumulativerate)) +
  geom_line()+
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  ylim(0,1) +
  theme_classic() +
  ggtitle("WSLS (self = 1) vs. Strategy 2 (other = 0)")

ggarrange(a,b, nrow = 2, ncol = 1)

ggsave("figures/outcome_1_agent_wsls_vs_strategy_2.png")
```

## Strategy 1 vs. Strategy 2

```{r}
# strategy 1 (self) vs. strategy 2 (other)
Self <- rep(NA, trials)
Other <- rep(NA, trials)

Self[1] <- RandomAgent_f(1, 0.5)
Other[1] <- RandomAgent_f(1, 0.5)

Self[2] <- RandomAgent_f(1, 0.5)
Other[2] <- strategy_2(prevChoice = Other[1], Feedback = 1 - ifelse(Self[1] == Other[1], 1, 0), noise = 0.1)

for (i in 3:trials) {
  if (Self[i - 1] == Other[i - 1]) {
    feedback_1 = 1
  } else {feedback_1 = 0}
  if (Self[i - 2] == Other[i - 2]) {
    feedback_2 = 1
  } else {feedback_2 = 0}
  Self[i] <- strategy_1(Self[i - 1], Self[i - 2], feedback_1 = feedback_1, feedback_2 = feedback_2, rate = 0.5, noise = 0.1)
  Other[i] <- strategy_2(prevChoice = Other[i-1], Feedback = 1 - feedback_1, noise = 0.1)
}

sum(Self == Other)

df <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

df <- df %>% 
  mutate(cumulativerate = cumsum(Feedback)/seq_along(Feedback))

a <- ggplot(df) + theme_classic() +
  geom_line(color = "red", aes(trial, Self)) +
  geom_line(color = "blue", aes(trial, Other))  +
  ggtitle("Strategy 1 (self) vs. Strategy 2 (other)")

b <- df %>% 
  ggplot(aes(x = trial, y = cumulativerate)) +
  geom_line()+
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  ylim(0,1) +
  theme_classic()  +
  ggtitle("Strategy 1 (self = 1) vs. Strategy 2 (other = 0)")

ggarrange(a,b, nrow = 2, ncol = 1)

ggsave("figures/outcome_1_agent.png")
```

# Simulating 100 pairs of agents for Strategy 1 vs. Strategy 2

```{r}
df_1_vs_2 <- NULL

for (j in 1:agents){
  Self <- rep(NA, trials)
  Other <- rep(NA, trials)
  
  Self[1] <- RandomAgent_f(1, 0.5)
  Other[1] <- RandomAgent_f(1, 0.5)
  
  Self[2] <- RandomAgent_f(1, 0.5)
  Other[2] <- strategy_2(prevChoice = Other[1], Feedback = 1 - ifelse(Self[1] == Other[1], 1, 0), noise = 0.1)
  
  for (i in 3:trials) {
    if (Self[i - 1] == Other[i - 1]) {
      feedback_1 = 1
    } else {feedback_1 = 0}
    if (Self[i - 2] == Other[i - 2]) {
      feedback_2 = 1
    } else {feedback_2 = 0}
    Self[i] <- strategy_1(Self[i - 1], Self[i - 2], feedback_1 = feedback_1, feedback_2 = feedback_2, rate = 0.5, noise = 0.1)
    Other[i] <- strategy_2(prevChoice = Other[i-1], Feedback = 1 - feedback_1, noise = 0.1)
  }
  
  temp <- tibble(trial = seq(trials), feedback = ifelse(Self == Other, 1, 0), agent = j)
  
  df_1_vs_2 <- rbind(df_1_vs_2, temp)
}

df_1_vs_2 <- df_1_vs_2 %>% 
  group_by(agent) %>% 
  mutate(cumulativerate = cumsum(feedback)/seq_along(feedback))

df_1_vs_2 %>% 
  ggplot(aes(x = trial, y = cumulativerate)) +
  geom_line()+
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  ylim(0,1) +
  theme_classic()  +
  ggtitle("Strategy 1 (self = 1) vs. Strategy 2 (other = 0)")

ggsave("figures/outcome_100_agents.png")

df_1_vs_2 %>% 
  group_by(trial) %>% 
  mutate(mean_cumrate = mean(cumulativerate), sd_cumrate = sd(cumulativerate)) %>%
  ggplot(aes(x = trial)) +
  geom_line(aes(y = mean_cumrate))+
  geom_ribbon(aes(y = mean_cumrate, ymin = mean_cumrate - sd_cumrate, ymax = mean_cumrate + sd_cumrate), alpha = 0.2)+
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  ylim(0,1) +
  theme_classic()  +
  ggtitle("Strategy 1 (self = 1) vs. Strategy 2 (other = 0)")

ggsave("figures/mean_outcome_100_agents.png")
```

